### 2019-08-22 manuscript/abstract.tex
edited summary (Boris please check)

\item We show that the effect of ploidy on diversification can be largely explained by its correlation with breeding system and additional unobserved factors changing diversification rates. %B: Why not just directly state here that the effect seems to be primarily explained by breeding system? (unaltered)
%These results are largely robust to allowing for diploidization.  %B: I now dropped it again to squeeze under 200 words. %B: this sentence was apparently accidentally dropped?
We also find that the most common evolutionary pathway to polyploidy in Solanaceae occurs via direct breakdown of self-incompatibility by whole-genome duplication, rather than indirectly via breakdown followed by polyploidization.

\item  Lineage diversification in Solanaceae appears to be the result of complex interactions among breeding system, ploidy, and unobserved factors. 
Examination of models that include trait interactions alongside `hidden' traits may generally enhance our understanding of diversification.  %B was: We show that modeling complex trait interactions is key to our understanding of diversification.       
\end{itemize}

>>>>

\item We show that the diversification patterns in Solanaceae can largely explained by changes in breeding system and additional unobserved factors linked to speciation and rates, even under the presence of ploidy information. %B: Why not just directly state here that the effect seems to be primarily explained by breeding system? (unaltered)
%These results are largely robust to allowing for diploidization.  %B: I now dropped it again to squeeze under 200 words. %B: this sentence was apparently accidentally dropped? % I removed the diploidization because the story was complicated so I preferred not to add it in the abstract
%R- Is the above sentence better now?

We also find that the most common evolutionary pathway to polyploidy in Solanaceae occurs via direct breakdown of self-incompatibility by whole-genome duplication, rather than indirectly via breakdown followed by polyploidization.

\item Comparing multiple stochastic diversification models that include complex trait interactions alongside hidden states enhances our understanding of the macroevolutionary patterns in plant phylogenies.  %B was: We show that modeling complex trait interactions is key to our understanding of diversification.       
\end{itemize}
